Fast and optimal centroiding of faint stars

### 2015-03-24 ms/figure.tex
Update figure.tex

Assuming
uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
of the $B\times B$Fisher matrix $\mathcal{F}_{ij}$ are given by
\beq
\mathcal{F}_{ij} = \sum_{m}\frac{1}{\sigma_{m}^{2}}\frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}}
\label{fisher}
\eeq

>>>>

Assuming
uncorrelated Gaussian error $\sigma_{m}$ for each observable $f_{m}$, elements
of the $B\times B$ Fisher matrix $\mathcal{F}_{ij}$ are given by
\beq
\mathcal{F}_{ij} = \sum_{m}\frac{1}{\sigma_{m}^{2}}\frac{\partial f_{m}}{\partial \theta_{i}}\frac{\partial f_{m}}{\partial \theta_{j}}
\label{fisher}
\eeq
